### 2020-03-04 main_text/main_text.tex
Correct typos and new figure 10

	\begin{figure}%[h!]
		\centering
		\includegraphics{media/Fig10_bifurcation.eps}
		\caption{{\bf Bifurcation diagram showing the hysteresis loop in the stochastic system.}
			The blue line shows the positions of the deterministic fixed
			points, while the dashed line indicates the instability of
			the middle one. The orange and yellow points show the mean
			of the stochastic simulations when started at zero and at
			the high fixed point, respectively. The positions of the two
			peaks in the bimodal distributions are indicated by smaller
			points, connected by dotted lines. To make this clearer, the
			bimodal distributions themselves are shown in a light color (in a smoothed form). The arrows illustrate the
			hysteresis loop in the stochastic simulations.
			}
		\label{fig10:Bifurcation}
	\end{figure}

@@

	\subsection*{Materials and Methods}
	\paragraph*{Bacterial Strains.} Strains used in this work
	derive from {\it E. coli} K12 MG1655 with the {\it lac} operon
	removed and were constructed similarly to those used in
	\cite{RazoMejia 2018, Belliveau2019}. $\Delta{xapAB}$ and
	$\Delta{xapABR}$ knockouts were generated using the approach of
	Datsenko and Wanner \cite{Datsenko2000}. For the fluorescent
	reporter constructs the {\it xapAB} promoter region, with one or
	both XapR binding sites, were extracted from {\it E. coli} K12
	MG1655 by PCR. These were cloned into the YFP-expressing reporter
	plasmid pZS25,  containing kanamycin resistance, and integrated at
	the {\it galK} locus using $\lambda$ Red recombineering \cite{Sharan2009}.

	\paragraph*{Flow Cytometry Measurements.}
	Experimental measurements in Fig. 2B of the main text were obtained
	via flow cytometry and were performed in a similar manner as
	described in~\cite{RazoMejia2018}. Briefly, wild-type,
	$\Delta{xapABR}$, and $\Delta{xapAB}$ were grown to saturation in
	rich LB Miller (BD Medical) medium and were diluted 1:1000 into M9
	minimal medium supplemented with 0.5\% (w/v) glucose and the
	appropriate concentration of xanthosine. For measurements of the
	$\Delta{xapAB}$ strain, chloramphenicol was also added to the growth
	medium to ensure stability of the pZ3PN25-tetR plasmid along with 10
	ng /mL of anhydro-tetracycline to maximize expression of
	xapR-mCherry. Cultures were allowed to grow at 37$^\circ$ C for six
	to eight hours to an OD$_{600nm}$ of $\approx$ 0.3 At this point,
	the cultures were diluted 1:10 into M9 + 0.5\% glucose and were
	immediately analyzed via a MacsQuant VYB Flow Cytometery
	(MiltenyiBiotec). Measurement files were exported to CSV file
	formats and analyzed as previously described
	in~\cite{RazoMejia2018}.

>>>>

	\begin{figure}%[h!]
		\centering
		\includegraphics{media/Fig10_bifurcation.eps}
		\caption{{\bf Bifurcation diagram showing the hysteresis loop in the stochastic system.}
			The blue line shows the positions of the deterministic fixed
			points, while the dashed line indicates the instability of
			the middle one. The orange and yellow points show the mean
			of the stochastic simulations when started at zero and at
			the high fixed point, respectively. The positions of the two
			peaks in the bimodal distributions are indicated by smaller
			points, connected by dotted lines. To make this clearer, the
			bimodal distributions themselves are shown on the right. The arrows illustrate the
			hysteresis loop in the stochastic simulations.
			}
		\label{fig10:Bifurcation}
	\end{figure}

@@

	\subsection*{Materials and Methods}
	\paragraph*{Bacterial Strains.} Strains used in this work
	derive from {\it E. coli} K12 MG1655 with the {\it lac} operon
	removed and were constructed similarly to those used in
	\cite{RazoMejia2018, Belliveau2019}. $\Delta{xapAB}$ and
	$\Delta{xapABR}$ knockouts were generated using the approach of
	Datsenko and Wanner \cite{Datsenko2000}. For the fluorescent
	reporter constructs the {\it xapAB} promoter region, with one or
	both XapR binding sites, were extracted from {\it E. coli} K12
	MG1655 by PCR. These were cloned into the YFP-expressing reporter
	plasmid pZS25,  containing kanamycin resistance, and integrated at
	the {\it galK} locus using $\lambda$ Red recombineering \cite{Sharan2009}.

	\paragraph*{Flow Cytometry Measurements.}
	Experimental measurements in Fig. 2B of the main text were obtained
	via flow cytometry and were performed in a similar manner as
	described in~\cite{RazoMejia2018}. Briefly, wild-type,
	$\Delta{xapABR}$, and $\Delta{xapAB}$ were grown to saturation in
	rich LB Miller (BD Medical) medium and were diluted 1:1000 into M9
	minimal medium supplemented with 0.5\% (w/v) glucose and the
	appropriate concentration of xanthosine. For measurements of the
	$\Delta{xapAB}$ strain, chloramphenicol was also added to the growth
	medium to ensure stability of the pZ3PN25-tetR plasmid along with 10
	ng /mL of anhydro-tetracycline to maximize expression of
	xapR-mCherry. Cultures were allowed to grow at 37$^\circ$ C for six
	to eight hours to an OD$_{600nm}$ of $\approx$ 0.3. At this point,
	the cultures were diluted 1:10 into M9 + 0.5\% glucose and were
	immediately analyzed via a MacsQuant VYB Flow Cytometery
	(MiltenyiBiotec). Measurement files were exported to CSV file
	formats and analyzed as previously described
	in~\cite{RazoMejia2018}.
